Summer 2024 Report

### 2024-12-12 Relations/Report.tex
Minor tidying of ars
Cleaning up the useful dead ends section

\end{center}
Counterexample to:
\begin{itemize}
  \item WCR $\implies$ CR
  \item WCR and WN $\implies$ CR
  \item WCR and WN $\implies$ SN
  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP)}
\end{itemize}
\subsection*{Counterexample 2}
\begin{center}
  \begin{tikzcd}
      % Nodes
      \node (x) {a};
      \node (n) [left of=x, xshift=-1cm] {n \in NF};
      \node (y) [right of=x, xshift=1cm] {b};
      \node (z) [right of=y] {c};

@@

\subsection*{Counterexample 3}

@@

\subsection*{Counterexample 4}
An infinite sequence
  \begin{center}
      \begin{tikzpicture}
      % Define the nodes
      \node (a) at (0, 0) {$f_0$};
      \node (b) at (1, 0) {$f_1$};
      \node (dots) at (2, 0) {$...$};

@@

\subsection*{Counterexample 5}
An infinite sequence with a bound that is a normal form.
\begin{center}

@@

    \end{center}
Counterexample to:
\begin{itemize}
  \item WN $\implies$ SN
  \item WN and CR $\implies$ SN
  \item WN, CR and, bounded $\implies$ SN
\end{itemize}

\subsection*{Counterexample 6}
An infinite sequence with a bound that is a normal form where each element
of the sequence has a single step relation to the initial element of the sequence.
\begin{center}
  \begin{tikzpicture}
      % Define the nodes inside the region f
      \node (f0) at (0, 0) {$f_0$};
      \node (f1) at (1, 0) {$f_1$};
      \node (dots) at (2, 0) {$...$};

@@

\subsection*{Counterexample 7}
An "infinite haircomb"
\begin{center}
  \begin{tikzpicture}
      % Define the nodes inside the region f
      \node (f0) at (0, 0) {$f_0$};
      \node (f1) at (1, 0) {$f_1$};
      \node (f2) at (2, 0) {$f_2$};
      \node (dots) at (3, 0) {$...$};

@@

        \item Does UN-lemma \emph{require} the decidability assumption?
      \end{itemize}
    \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
    for example,
    \begin{itemize}
      \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
      \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
    \end{itemize}
    \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
      be related to the cofinality property.
      \item What happens if properties involving sequences are reformulated for
    $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
    \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
    \item Knaster--Tarski in a well-founded setting: what additional
    hypotheses are necessary?
    \item Show SN and WNFP $\to$ CR : SN R $to$ WNFP R $to$ CR R (or, what combination of properties with WNFP gets us to CR)
    \item Major: Find a classical or constructive solution to theorem 1-2-3 ii. Note, we have a counterexample showing that we 
    cannot solve this whilst using recurrence property and boundedness rather than ind(uctive) and inc(reasing). The counterexample is the self loop on an element. 
    \item is $\omega$-bounded implied by WN and the following confluence property:
    $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $. (This is a weaker form of WNFP)
  \end{enumerate}

>>>>

\end{center}
Counterexample to:
\begin{itemize}
  \item WCR $\implies$ CR
  \item WCR  $\implies$ WNFP
  \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ R a c $\to$ (R *) c b }
  \item WCR and WN $\implies$ CR
  \item WCR and WN $\implies$ SN
  \item IOW and WCR $\implies$ WNFP \sacomment{We need to define these still (IOW and WNFP) in the report}
\end{itemize}

\subsection*{Counterexample 2}
\begin{center}
  \begin{tikzcd}
      % Nodes
      \node (x) {a};
      \node (n) [left of=x, xshift=-1cm] {n \in NF};
      \node (y) [right of=x, xshift=1cm] {b};
      \node (z) [right of=y] {c};

      % Arrows
      \draw[->] (x) -- (n);
      \draw[->] (x) -- (y);
      \draw[->] (y) to [bend left] (z);
      \draw[->] (z) to [bend left] (y);
  \end{tikzcd}
\end{center}

Counterexample to:
\begin{itemize}
  \item WCR and an increasing sequence where the first elelement of the sequence reduces to an element in normal form $\to$ 
  the sequence is bounded.
\end{itemize}

\subsection*{Counterexample 3}
\begin{center}
  \begin{tikzcd}
      % Nodes
      \node (x) {a};
      \node (n) [left of=x, xshift=-1cm] {n \in NF};
      \node (y) [right of=x, xshift=1cm] {b};
      \node (z) [right of=y] {c};

@@

\subsection*{Counterexample 4}

@@

\subsection*{Counterexample 5}
An infinite sequence
  \begin{center}
      \begin{tikzpicture}
      % Define the nodes
      \node (a) at (0, 0) {$f_0$};
      \node (b) at (1, 0) {$f_1$};
      \node (dots) at (2, 0) {$...$};

@@

\subsection*{Counterexample 6}
An infinite sequence with a bound that is a normal form.
\begin{center}

@@

    \end{center}
Counterexample to:
\begin{itemize}
  \item WN $\implies$ SN
  \item WN and CR $\implies$ SN
  \item WN, CR, and bounded $\implies$ SN
  \item WN, UN, and bounded $implies$ SN 
\end{itemize}

\subsection*{Counterexample 7}
An infinite sequence with a bound that is a normal form where each element
of the sequence has a single step relation to the initial element of the sequence.
\begin{center}
  \begin{tikzpicture}
      % Define the nodes inside the region f
      \node (f0) at (0, 0) {$f_0$};
      \node (f1) at (1, 0) {$f_1$};
      \node (dots) at (2, 0) {$...$};

@@

\subsection*{Counterexample 8}
An "infinite haircomb"
\begin{center}
  \begin{tikzpicture}
      % Define the nodes inside the region f
      \node (f0) at (0, 0) {$f_0$};
      \node (f1) at (1, 0) {$f_1$};
      \node (f2) at (2, 0) {$f_2$};
      \node (dots) at (3, 0) {$...$};

@@

        \item Does UN-lemma \emph{require} the decidability assumption?
      \end{itemize}
    \item META questions: Which of the ARS theorems can be made ``local/pointwise'',
    for example,
    \begin{itemize}
      \item NL+: $WCR(R) \land SN(x) \to CR(x)$?  (Yes?)
      \item NL++: $WCR(x) \land SN(x) \to CR(x)$? (No.)
    \end{itemize}
    \item Can "sequential" properties like RP, RP-, isWFseq, isWFseq-, $\omega$-bounded, etc.,
      be related to the cofinality property.
      \item What happens if properties involving sequences are reformulated for
    $R^r$? (Cannot decide whether the given sequence is finite or infinite.)
    \item Knaster-Tarski Lemma: Most general form? Alternative formulations?
    \item Knaster--Tarski in a well-founded setting: what additional
    hypotheses are necessary?
    \item Show SN and WNFP $\to$ CR : SN R $to$ WNFP R $to$ CR R (or, what combination of properties with WNFP gets us to CR)
    \item Major: Find a classical or constructive solution to theorem 1-2-3 ii. Note, we have a counterexample showing that we 
    cannot solve this whilst using recurrence property and boundedness rather than ind(uctive) and inc(reasing). The counterexample is the self loop on an element. 
    \item is $\omega$-bounded implied by WN and the following confluence property:
    $a \to^* n \in NF$, and $a \to b$ then $b \to^* n $. (This is a weaker form of WNFP)
    \item WN and WCR $\to$ bounded. We reached a dead end trying to show this before. Check github history in the ARS file for iii-lemma 
    if you'd like to see the previous direction.
  \end{enumerate}
